---
title: "Insight into Movie Ratings data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
```

### Load data

```{r load-data}
setwd("F:\\Online Course\\R Programming (Udemy)\\Section6")
mov <- read.csv("Section6-Homework-Data.csv")
```

### Exploring data frame

head(mov) #top rows
summary(mov) #column summaries
str(mov) #structure of the dataset

* * *

## Cleaning the data

```{r warning=FALSE}
filt <- (mov$Genre == "action") | (mov$Genre == "adventure") | (mov$Genre == "animation") | (mov$Genre == "comedy") | (mov$Genre == "drama")

filt2 <- (mov$Studio == "Buena Vista Studios") | (mov$Studio == "WB") | (mov$Studio == "Fox") | (mov$Studio == "Universal") | (mov$Studio == "Sony") | (mov$Studio == "Paramount Pictures")

mov2 <- mov[filt & filt2,]
```

### Constructing the plot
```{r warning=FALSE}
p <- ggplot(data=mov2, aes(x=Genre, y=Gross...US)) + 
        geom_jitter(aes(size=Budget...mill., colour=Studio)) + 
        geom_boxplot(alpha=0.7, outlier.color = NA) +
        xlab("Genre") +
        ylab("Gross % US") +
        ggtitle("Domestic Gross % by Genre") + 
        theme(
          text = element_text(family="Comic Sans MS"),
          axis.title.x = element_text(colour="Blue", size=12),
          axis.title.y = element_text(colour="Blue", size=12),
          axis.text.x = element_text(size=10),
          axis.text.y = element_text(size=10),
          plot.title = element_text(colour="Black", size=15),
          legend.title = element_text(size=12),
          legend.text = element_text(size=10)
        )
p$labels$size = "Budget $M"
p

```

### The data story
We can see that Action genre has been popular among all genres with most number of movies, and drama is the least popular genre. Almost 40-50% of the gross comes from US region in all the genres.

### A cool insight
```{r}
ggplot(data=mov, aes(x=Day.of.Week)) + geom_bar()

##Notice? No movies are released on a Monday. Ever.
```